\documentclass[a4paper,10pt]{article}
\usepackage[top=0.8in,bottom=1in,left=1in,right=1in]{geometry}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{titlesec}
\usepackage{parskip}

% Formatting for section titles
\titleformat{\section}{\large\bfseries}{}{0em}{}
\titlespacing*{\section}{0pt}{1.5ex plus .1ex minus 0.1ex}{1ex plus .1ex}

\setlength{\parindent}{0pt}

\begin{document}

\begin{center}
    {\LARGE \bfseries DHIRAJ KUMAR VANDRANGI} \\
    \vspace{0.3em}
    Senior Software Engineer / Team Lead \\
    \vspace{0.2em}
    {\small Phone: +91 96524 85082 \quad
    Email: \href{mailto:dhirajkumarvandrangi@gmail.com}{dhirajkumarvandrangi@gmail.com}} \\
    {\small LinkedIn: \href{https://www.linkedin.com/in/dhiraj-kumar-2450a6106}{dhiraj-kumar-2450a6106} \quad
    GitHub: \href{https://github.com/Dhirajkumar13}{Dhirajkumar13}}
\end{center}

\vspace{-2mm}
\noindent\makebox[\linewidth]{\rule{\linewidth}{0.4pt}}

% ===================== PROFESSIONAL SUMMARY =====================
\section*{Professional Summary}
Senior Software Engineer with 7+ years of experience in backend and full-stack development, specializing in Node.js, Express.js, MongoDB, RESTful API design, and scalable microservices. Strong experience building secure APIs, implementing authentication and authorization using JWT, and optimizing backend performance. Hands-on experience with AWS cloud services, serverless components, CI/CD pipelines, and production support, along with application-level Generative AI integrations using OpenAI and Azure OpenAI. Proven Team Lead with Agile delivery, code review ownership, and end-to-end system responsibility.

\vspace{-2mm}
\noindent\makebox[\linewidth]{\rule{\linewidth}{0.4pt}}

% ===================== TECHNICAL SKILLS =====================
\section*{Technical Skills}
\begin{itemize}[leftmargin=*,itemsep=0.2em]
    \item \textbf{Backend / Platform:} Node.js, Express.js, TypeScript, RESTful API Design, Microservices Architecture, MVC Architecture, Secure APIs, Authentication \& Authorization (JWT), WebSocket, Socket.IO, Performance Optimization, Scalability
    \item \textbf{Frontend:} HTML, CSS, JavaScript, jQuery, React.js
    \item \textbf{Databases:} MongoDB (primary), MySQL, PostgreSQL, Data Modeling, Schema Design, Indexing, Query Optimization
    \item \textbf{Cloud / DevOps:} AWS (S3, Lambda, API Gateway, EC2, RDS, SNS, SQS, IAM, CloudWatch, VPC), Serverless Architecture, CI/CD Pipelines (Bitbucket), Load Balancing
    \item \textbf{Generative AI:} OpenAI API, Azure OpenAI, Prompt Engineering, Conversational AI, Document Summarization, Semantic Search
    \item \textbf{Process:} Agile, Scrum, SDLC, Code Reviews, Production Support
\end{itemize}

\vspace{-2mm}
\noindent\makebox[\linewidth]{\rule{\linewidth}{0.4pt}}

% ===================== PROFESSIONAL EXPERIENCE =====================
\section*{Professional Experience}

\textbf{Kairos Technologies Inc.} \hfill Aug 2018 -- Present \\
\textit{Senior Software Engineer / Team Lead}

\begin{itemize}[leftmargin=*,itemsep=0.2em]
    \item Designed and developed scalable backend systems using Node.js, Express.js, and MongoDB following microservices and MVC architecture.
    \item Led API design and development for secure RESTful services with JWT-based authentication and authorization.
    \item Built and maintained secure APIs supporting chatbot platforms, document-processing pipelines, and automation systems.
    \item Improved backend performance and system reliability by optimizing MongoDB queries, implementing indexing strategies, and refining data models.
    \item Implemented cloud-native solutions on AWS including S3-based storage, SES email automation, and CloudWatch monitoring.
    \item Implemented serverless components using AWS Lambda for event-driven processing and automation workflows.
    \item Contributed to CI/CD pipelines using Bitbucket for automated builds and deployments.
    \item Integrated Generative AI APIs (OpenAI / Azure OpenAI) into Node.js services for chatbot responses, multilingual conversations, document summarization, and semantic search.
    \item Developed React-based admin dashboards and internal tools for workflow and system management.
    \item Integrated third-party platforms including Salesforce, Genesys Cloud, WhatsApp APIs, and email services.
    \item Provided production support, logging, monitoring, and incident resolution for live systems.
    \item Led code reviews, mentored junior developers, and ensured Agile/Scrum best practices across the team.
\end{itemize}

\vspace{-2mm}
\noindent\makebox[\linewidth]{\rule{\linewidth}{0.4pt}}

% ===================== KEY PROJECTS =====================
\section*{Key Projects}
\vspace{0.5em}

\textbf{Western Union -- Chatbot Platform (Lisa)} \\
\vspace{-5mm}
\begin{itemize}[leftmargin=*,itemsep=0.2em]
    \item Developed backend services integrating chatbot workflows with Salesforce and Genesys Cloud for live-agent escalation.
    \item Built WhatsApp chatbot APIs and real-time messaging services using Socket.IO.
    \item Implemented secure API layers with authentication and structured error handling.
    \item Implemented Google reCAPTCHA validation to prevent bot abuse and enhance security for public-facing chatbot APIs.
    \item Integrated Generative AI for conversation summarization and multilingual chatbot responses.
\end{itemize}

\vspace{1em}

\textbf{Skil.AI -- Automation \& Document Intelligence Platform (NextCX.ai \& Docubaat)} \\
\vspace{-5mm}
\begin{itemize}[leftmargin=*,itemsep=0.2em]
    \item Designed and implemented document ingestion and automation pipelines using Node.js, AWS S3, and FTP workflows.
    \item Built REST APIs for document upload, parsing, storage, and semantic search.
    \item Integrated AI-powered document summarization and search using OpenAI APIs.
    \item Developed React-based admin interfaces for workflow and chatbot configuration management.
    \item Improved system performance and response times through backend optimization.
\end{itemize}

\vspace{0.5em}

\textbf{Itech -- Automated Document Processing System} \\
\vspace{-5mm}
\begin{itemize}[leftmargin=*,itemsep=0.2em]
    \item Built backend automation for extracting structured data from uploaded documents.
    \item Developed REST APIs for workflow orchestration and report generation.
    \item Implemented secure document storage using AWS S3 with automated email notifications.
\end{itemize}

\vspace{0.5em}

\textbf{Online Visas -- Immigration Automation Platform} \\
\vspace{-5mm}
\begin{itemize}[leftmargin=*,itemsep=0.2em]
    \item Developed backend services for document data extraction and workflow automation.
    \item Integrated email systems, Excel processing, and cloud storage pipelines for automated operations.
\end{itemize}

\vspace{-2mm}
\noindent\makebox[\linewidth]{\rule{\linewidth}{0.4pt}}

% ===================== EDUCATION =====================
\section*{Education}
\textbf{Bachelor of Technology (B.Tech) -- Computer Science Engineering}, GITAM University \hfill 2018 \\
\noindent\makebox[\linewidth]{\rule{\linewidth}{0.4pt}}

% ===================== AWARDS =====================
\section*{Awards \& Recognition}
\begin{itemize}[leftmargin=*,itemsep=0.2em]
    \item Exemplary Executor -- Delivery Excellence Award (2024)
    \item Best Employee of the Year (2022)
    \item Achiever Award -- Junior Level (2019)
\end{itemize}
\noindent\makebox[\linewidth]{\rule{\linewidth}{0.4pt}}
\end{document}
